\section{Related Work}

There is a vast amount of work on 
side channel 
detection~\cite{182946, 236338, Brotzman19Casym, 203878,217537,Wichelmann:2018:MFF:3274694.3274741,langley2010ctgrind}, 
  %side channel
mitigation~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344,shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting}, 
and information
quantification~\cite{10.1007/978-3-642-31424-7_40,McCamantE2008,5207642,Phan:2012:SQI:2382756.2382791,Chattopadhyay:2017:QIL:3127041.3127044}, 
Here we only present the closely related work to ours.
Due to space limit, we do not include side channel attack work.

\subsection{Detection}

There are a large number of works on side-channel vulnerability detections in
recent years.  CacheAudit~\cite{182946} uses abstract domains to compute the
over approximation of cache-based side-channel information leakage upper bound.
However, due to over approximation they make, CacheAudit can indicate the
program is side-channel free if the program has zero leakage.  However, it is
less useful to judge the sensitive level of the side-channel leakage based on
the leakage provided by CacheAudit. CacheS~\cite{236338} improves the work of
CacheAudit by proposing the novel abstract domains, which only track
secret-related code. Like CacheAudit, CacheS cannot provide the information to
indicate the sensitive level of side-channel vulnerabilities.
CacheSym~\cite{Brotzman19Casym} introduces a static cache-aware symbolic
reasoning technique to cover multiple paths for the target program. Still, their
approaches cannot assess the sensitive level for each side-channel
vulnerability.

The dynamic approach, usually comes with taint analysis and symbolic execution,
can perform a very precise analysis. CacheD~\cite{203878} takes a concrete
program execution trace and run the symbolic execution on the top of the trace
to get the formula of each memory address. During the symbolic execution, every
value except the sensitive key uses the concrete value. Therefore, CacheD is
quite precise in term of false positives. We adopted a similar idea to model the
secret-dependent memory accesses. DATA~\cite{217537} detects address-based
side-channel vulnerabilities by comparing different execution traces under
various test inputs. MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses
mutual information (MI) between sensitive input and execution state to detect
side-channels. They can only detect control-flow channels and MI scores are less
meaningful for dynamic analysis.

\subsection{Mitigation}
Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting} side-channels mitigation methods have
been proposed recently. Hardware countermeasures, including parting the hardware
computing resource~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, which need to change the hardware and is
usually hard to adopt in reality. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} introduced a compiler-based approach
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice}, unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

\subsection{Quantification}

Quantitative Information Flow (QIF) aims at providing an information leakage
estimation for the sensitive information given the public output. If zero bit
of the information is leaked, the program is called non-interference. McCamant
and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
flow capacity. Backes et al.~\cite{5207642} proposes an automated method for QIF
by computing an equivalence relation on the set of input keys. But the approach
cannot handle real-world programs with bitwise operations. Phan et
al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
work is to ensure the program is non-interference. They adopt an over
approximation way of estimating the total information leakage and their method
does not work for secret-dependent memory access side-channels.
CHALICE~\cite{Chattopadhyay:2017:QIL:3127041.3127044} quantifies the leaked
information for a given cache behavior. CHALICE symbolically reason about cache
behavior and estimate the amount of leaked information based on cache miss/hit.
Their approach can only scale to small programs, which limits its usage in
real-world applications. On the contrary, \tool{} can assess the sensitive level
of side-channels with different granularities. It can also analyze side-channels
in real-world crypto libraries.



